The Proofs

### 2024-08-04 paper/tex/01-introduction.tex
fix refs

In this paper, we extend the local type inference algorithm to a language with
both universal and existential quantifiers, which can both be instantiated
impredicatively. This extended system is referred to as \fexists. The
combination of features in \fexists  broke a number of the invariants which
traditional type inference algorithms depend on and required us to invent
new algorithms which combine both unification and (surprisingly)
anti-unification.

@@

\paragraph*{\textbf{Acknowledgments}} We would like to thank Meven
Lennon-Bertrand for his extremely helpful comments and suggestions.

>>>>

In this paper, we extend the local type inference algorithm to a language with
both universal and existential quantifiers, which can both be instantiated
impredicatively. This extended system is referred to as \fexists. 
The version of this system without existential quantifiers was studied 
by \citet{mercer2019:system-f}. However, the addition of existentials in \fexists
broke a number of the invariants that traditional type inference algorithms depend
 on and required us to invent new algorithms which combine both unification and 
 (surprisingly) anti-unification.

@@

### 2024-08-04 proofs/content.tex
fix capitalization
fix refs

% \renewcommand{\proofGenDir}{_gen}

@@

Notice that checking the well-formedness of a type
is an \emph{algorithmic} procedure, in which 
both the context and the type are considered inputs.
In other words, it is syntax-directed and mode-correct 
(according to \cite{dunfieldBidirectionalTyping2020}), 
which means that checking the well-formedness of a type
can be done recursively by a deterministic algorithm. 
We will use the well-formedness checking in the inference algorithm, 
for example, to check that the existential variables do not escape their scope.

\pagebreak[4]
\begin{algorithm}[Type Well-formedness]
  \label{alg:wf}
  \hfill\\
  \begin{minipage}[t]{0.45\textwidth}
    \ottdefnWFTNiWFLabeled{}
  \end{minipage}
  \begin{minipage}[t]{0.45\textwidth}
    \ottdefnWFTPiWFLabeled{}
  \end{minipage}
\end{algorithm}

@@

\begin{definition}[Declarative Subtyping and Equivalence]
  \label{def:subDOne}
  \hfill\\
  \begin{minipage}[t]{0.45\textwidth}
      \ottdefnDOneNsubLabeled{}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
      \ottdefnDOnePsupLabeled{}
  \end{minipage}

  \begin{minipage}[t]{0.45\textwidth}
      \ottdefnDOneNeqLabeled{}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.45\textwidth}
      \ottdefnDOnePeqLabeled{}
  \end{minipage}
\end{definition}

@@

  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnWFATNauWFLabeled{}
  \end{minipage}%
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnWFATPauWFLabeled{}
  \end{minipage}
\end{algorithm}

Algorithmic Type Contexts are used in the unification algorithm.
In the subtyping algorithm, 
the context needs to remember additional information.
In particular, each algorithmic variable is associated with a
context it must be instantiated in 
(i.e. the context in which the type replacing the variable must be well-formed).
This association is represented by \emph{instantiation context} $[[Θ]]$.
\begin{definition}[Instantiation context $[[Θ]]$]
  \hfill \\
  Instantiation context $[[Θ]]$ is represented by a set of 
  entries of form $[[ α̂⁺[Γ] ]]$ and $[[ α̂⁻[Γ] ]]$,
  where $[[α̂⁺]]$ and $[[α̂⁻]]$ are algorithmic variables,
  and $[[Γ]]$ is a context in which they must be instantiated.
  We assume that $[[Θ]]$ does not contain multiple entries for the same variable.

@@

  \begin{multicols}{2}
  \ottdefnEOneNeqLabeled{}
  \columnbreak\\
  \ottdefnEOnePeqLabeled{}
  \end{multicols}

@@

  \ottdefnONVarLabeled{}
  \newpage
  \ottdefnOPVarLabeled{}

@@

  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnNrmNNormLabeled{}
  \end{minipage}%
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnNrmPNormLabeled{}
  \end{minipage}

@@

  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnNrmuNNormLabeled{}
  \end{minipage}%
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnNrmuPNormLabeled{}
  \end{minipage}

@@

\begin{algorithm}[Subtyping]
  \label{alg:subtyping}
  \hfill\\
  \ottdefnANsubLabeled{}
  \ottdefnAPsupLabeled{}
\end{algorithm}

@@

\begin{definition}[Type Satisfying a Constraint Entry]
  \hfill\\
  \begin{multicols}{2}
  \ottdefnSATSCENLabeled{}
  \columnbreak\\
  \ottdefnSATSCEPLabeled{}
  \end{multicols}
\end{definition}

@@

  \ottdefnSCMELabeled\\
\end{algorithm}

@@

\begin{algorithm}[Unification]
  \hfill
  \begin{multicols}{2}
  \ottdefnUNUnifLabeled{}
  \columnbreak\\
  \ottdefnUPUnifLabeled{}
  \end{multicols}
\end{algorithm}

@@

\begin{algorithm}[The Least Upper Bound Algorithm]
  \hfill\\
  \ottdefnLUBNsubLabeled{}
\end{algorithm}

@@

\begin{algorithm}[Type Upgrade]
  \hfill\\
  \ottdefnLUBUpLabeled{}
\end{algorithm}

@@

  \ottdefnAUAUPLabeled{}
  \ottdefnAUAUNLabeled{}

@@

\begin{definition}[Declarative Type Inference]
  \hfill\\
  \label{def:declarative-typing}
  \ottdefnsDTLabeled
\end{definition}

@@

\begin{figure}
  \ottdefnSFtyLabeledTwoColumns{}
  \caption{Typing rules of \systemf}
  \label{fig:systemf-typing}
\end{figure}

\newpage
\begin{observation}
  The following rules are admissible in \systemf: \hfill\\
  \begin{minipage}{0.5\textwidth}
    \ottusedrule{\ottdruleSFtyAUnpackLabeled{}}
  \end{minipage}
  \begin{minipage}{0.5\textwidth}
    \ottusedrule{\ottdruleSFtyAPackLabeled{}}
    \ottusedrule{\ottdruleSFtyALetLabeled{}}
  \end{minipage}
\end{observation}

@@

\begin{figure}[t]
  \ottdefnELLabeled
  \caption{Subtyping elaboration from \fexists to \systemf}
  \label{fig:subt-elaboration}
\end{figure}

\clearpage
\begin{figure}[t]
  \ottdefnTELNLabeledTwoColumns{}

  \ottdefnTELPAppLabeled{}
  \caption{Typing elaboration from \fexists to \systemf}
  \label{fig:typing-elaboration}
\end{figure}
\clearpage

@@

\begin{figure}[t]
  \ottdefnELfPolLabeled{}
  \caption{Typing elaboration form from \systemf to \fexists}
  \label{fig:systemf-polarization}
\end{figure}

@@

\begin{algorithm}
  \hfill \\
  \ottdefnATPInfLabeled{}
  \hfill \\
  \ottdefnATNInfLabeled{}
  \hfill \\
  \ottdefnATSpinInfLabeled{}
\end{algorithm}

@@

The minimal instantiation algorithm is defined as follows:
\begin{algorithm}[Minimal Instantiation]
  \hfill \\
  \ottdefnSINGminInstLabeled{}
\end{algorithm}

@@

\begin{algorithm}[Singular Constraint Entry]
  \hfill\\
  \ottdefnSINGscEPLabeled{}
  \ottdefnSINGscENLabeled{}
\end{algorithm}

>>>>

% Add prefix to the labels so that they do not conflict with the main paper
\newcommand{\apppref}{:app}
\renewcommand{\ruleref}[1]{\nameref{\apppref#1}}

@@

Notice that checking the well-formedness of a type
is an \emph{algorithmic} procedure, in which 
both the context and the type are considered inputs.
In other words, it is syntax-directed and mode-correct 
(according to \citet{dunfield2020:bidirectional}), 
which means that checking the well-formedness of a type
can be done recursively by a deterministic algorithm. 
We will use the well-formedness checking in the inference algorithm, 
for example, to check that the existential variables do not escape their scope.

\pagebreak[4]
\begin{algorithm}[Type Well-formedness]
  \label{alg:wf}
  \hfill\\
  \begin{minipage}[t]{0.45\textwidth}
    \ottdefnWFTNiWFLabeled[\apppref]{}
  \end{minipage}
  \begin{minipage}[t]{0.45\textwidth}
    \ottdefnWFTPiWFLabeled[\apppref]{}
  \end{minipage}
\end{algorithm}

@@

\begin{definition}[Declarative Subtyping and Equivalence]
  \label{def:subDOne}
  \hfill\\
  \begin{minipage}[t]{0.45\textwidth}
      \ottdefnDOneNsubLabeled[\apppref]{}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
      \ottdefnDOnePsupLabeled[\apppref]{}
  \end{minipage}

  \begin{minipage}[t]{0.45\textwidth}
      \ottdefnDOneNeqLabeled[\apppref]{}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.45\textwidth}
      \ottdefnDOnePeqLabeled[\apppref]{}
  \end{minipage}
\end{definition}

@@

  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnWFATNauWFLabeled[\apppref]{}
  \end{minipage}%
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnWFATPauWFLabeled[\apppref]{}
  \end{minipage}
\end{algorithm}

Algorithmic Type Contexts are used in the unification algorithm.
In the subtyping algorithm, 
the context needs to remember additional information.
In particular, each algorithmic variable is associated with a
context it must be instantiated in 
(i.e. the context in which the type replacing the variable must be well-formed).
This association is represented by \emph{instantiation context} $[[Θ]]$.
\begin{definition}[Instantiation Context $[[Θ]]$]
  \hfill \\
  Instantiation context $[[Θ]]$ is represented by a set of 
  entries of form $[[ α̂⁺[Γ] ]]$ and $[[ α̂⁻[Γ] ]]$,
  where $[[α̂⁺]]$ and $[[α̂⁻]]$ are algorithmic variables,
  and $[[Γ]]$ is a context in which they must be instantiated.
  We assume that $[[Θ]]$ does not contain multiple entries for the same variable.

@@

  \begin{multicols}{2}
  \ottdefnEOneNeqLabeled[\apppref]{}
  \columnbreak\\
  \ottdefnEOnePeqLabeled[\apppref]{}
  \end{multicols}

@@

  \ottdefnONVarLabeled[\apppref]{}
  \newpage
  \ottdefnOPVarLabeled[\apppref]{}

@@

  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnNrmNNormLabeled[\apppref]{}
  \end{minipage}%
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnNrmPNormLabeled[\apppref]{}
  \end{minipage}

@@

  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnNrmuNNormLabeled[\apppref]{}
  \end{minipage}%
  \hfill
  \begin{minipage}[t]{0.48\textwidth}
    \ottdefnNrmuPNormLabeled[\apppref]{}
  \end{minipage}

@@

\begin{algorithm}[Subtyping]
  \label{alg:subtyping}
  \hfill\\
  \ottdefnANsubLabeled[\apppref]{}
  \ottdefnAPsupLabeled[\apppref]{}
\end{algorithm}

@@

\begin{definition}[Type Satisfying a Constraint Entry]
  \hfill\\
  \begin{multicols}{2}
  \ottdefnSATSCENLabeled[\apppref]{}
  \columnbreak\\
  \ottdefnSATSCEPLabeled[\apppref]{}
  \end{multicols}
\end{definition}

@@

  \ottdefnSCMELabeled[\apppref]\\
\end{algorithm}

@@

\begin{algorithm}[Unification]
  \hfill
  \begin{multicols}{2}
  \ottdefnUNUnifLabeled[\apppref]{}
  \columnbreak\\
  \ottdefnUPUnifLabeled[\apppref]{}
  \end{multicols}
\end{algorithm}

@@

\begin{algorithm}[The Least Upper Bound Algorithm]
  \hfill\\
  \ottdefnLUBNsubLabeled[\apppref]{}
\end{algorithm}

@@

\begin{algorithm}[Type Upgrade]
  \hfill\\
  \ottdefnLUBUpLabeled[\apppref]{}
\end{algorithm}

@@

  \ottdefnAUAUPLabeled[\apppref]{}
  \ottdefnAUAUNLabeled[\apppref]{}

@@

\begin{definition}[Declarative Type Inference]
  \hfill\\
  \label{def:declarative-typing}
  \ottdefnsDTLabeled[\apppref]{}
\end{definition}

@@

\begin{figure}
  \ottdefnSFtyLabeledTwoColumns[\apppref]{}
  \caption{Typing rules of \systemf}
  \label{fig:systemf-typing}
\end{figure}

\newpage
\begin{observation}
  The following rules are admissible in \systemf: \hfill\\
  \begin{minipage}{0.5\textwidth}
    \ottusedrule{\ottdruleSFtyAUnpackLabeled[\apppref]{}}
  \end{minipage}
  \begin{minipage}{0.5\textwidth}
    \ottusedrule{\ottdruleSFtyAPackLabeled[\apppref]{}}
    \ottusedrule{\ottdruleSFtyALetLabeled[\apppref]{}}
  \end{minipage}
\end{observation}

@@

\begin{figure}[t]
  \ottdefnELLabeled[\apppref]
  \caption{Subtyping elaboration from \fexists to \systemf}
  \label{fig:subt-elaboration}
\end{figure}

\clearpage
\begin{figure}[t]
  \ottdefnTELNLabeledTwoColumns[\apppref]{}

  \ottdefnTELPAppLabeled[\apppref]{}
  \caption{Typing elaboration from \fexists to \systemf}
  \label{fig:typing-elaboration}
\end{figure}
\clearpage

@@

\begin{figure}[t]
  \ottdefnELfPolLabeled[\apppref]{}
  \caption{Typing elaboration form from \systemf to \fexists}
  \label{fig:systemf-polarization}
\end{figure}

@@

\begin{algorithm}
  \hfill \\
  \ottdefnATPInfLabeled[\apppref]{}
  \hfill \\
  \ottdefnATNInfLabeled[\apppref]{}
  \hfill \\
  \ottdefnATSpinInfLabeled[\apppref]{}
\end{algorithm}

@@

The minimal instantiation algorithm is defined as follows:
\begin{algorithm}[Minimal Instantiation]
  \hfill \\
  \ottdefnSINGminInstLabeled[\apppref]{}
\end{algorithm}

@@

\begin{algorithm}[Singular Constraint Entry]
  \hfill\\
  \ottdefnSINGscEPLabeled[\apppref]{}
  \ottdefnSINGscENLabeled[\apppref]{}
\end{algorithm}

### 2024-08-04 proofs/tex/norm-lemmas.tex
fix refs

\lemmaNormSoundness*
\begin{proof}
  Mutual induction on $[[nf(iN) = iM]]$ and $[[nf(iP) = iQ]]$.
  Let us consider how this judgment is formed:
  \begin{caseof}
    \item{\nameref{\ottdruleNrmNVarLabel} and \nameref{\ottdruleNrmPVarLabel}}\\ By
      the corresponding equivalence rules.
    \item{\nameref{\ottdruleNrmShiftULabel}, \nameref{\ottdruleNrmShiftDLabel},
        and \nameref{\ottdruleNrmArrowLabel}}\\
      By the induction hypothesis and the corresponding congruent equivalence rules.
    \item{\nameref{\ottdruleNrmForallLabel}}, i.e. $[[nf(∀pas.uN) = ∀pas'.uN']]$ \label{case:norm-soundness:forall}\\
      From the induction hypothesis, we
      know that $[[iN ≈ iN']]$. In particular, by \cref{lemma:equiv-fv}, $[[fv
        iN]] \equiv [[fv iN']]$.
      Then by \cref{lemma:ord-soundness}, $[[{pas'}]]
      \equiv [[{pas} ∩ fv iN']] \equiv [[{pas} ∩ fv iN]]$, and thus,
      $[[{pas'} ∩ fv iN']] \equiv [[{pas} ∩ fv iN]]$.

      To prove $[[∀pas.iN ≈ ∀pas'.iN']]$, it suffices to provide a bijection 
      $\mu : [[{pas'} ∩ fv iN']] \leftrightarrow [[{pas} ∩ fv iN]]$ such that
      $[[iN ≈ [mu]iN']]$. Since these sets are equal, we take $\mu = id$.
    \item{\nameref{\ottdruleNrmExistsLabel}} Same as for \cref{case:norm-soundness:forall}.
  \end{caseof}
\end{proof}

@@

\lemmaNormalizationCompleteness*
\begin{proof}
  Mutual induction on $[[iN ≈ iM]]$ and $[[iP ≈ iQ]]$.
  \begin{caseof}
  \item {\nameref{\ottdruleEOneForallLabel}} \label{case:ord-completeness:forall}
   From the normalization definition,
    \begin{itemize}
      \item $[[nf(∀pas.iN)]] = [[∀pas'.nf(iN)]]$ where $[[pas']]$ is $[[ord {pas} in nf(iN)]]$
      \item $[[nf(∀pbs.iM)]] = [[∀pbs'.nf(iM)]]$ where $[[pbs']]$ is $[[ord {pbs} in nf(iM)]]$
    \end{itemize}
    Let us take $[[mu : ({pbs} ∩ fv iM) ↔ ({pas} ∩ fv iN)]]$ from the
    inversion of the equivalence judgment. Notice that from
    \cref{lemma:fv-nf,lemma:ord-soundness}, the domain and the codomain of $\mu$ can be written
    as $[[mu : {pbs'} ↔ {pas'}]]$.

@@

    \item[(ii)] 
    \begin{align*} 
      [[ [mu]pbs' ]] &= [[ [mu] ord {pbs} in nf(iM) ]]
                      && \text{by the definition of $[[pbs']]$ } \\
                      &= [[ [mu] ord ({pbs} ∩ fv iM) in nf(iM) ]]
                      && \text{from \cref{lemma:fv-nf,corollary:ord-weakening} } \\
                      &= [[ ord [mu] ({pbs} ∩ fv iM) in [mu] nf(iM) ]]
                      && \text{by \cref{lemma:distr-mu-ord}, because}\\
      &  \omit\rlap{\hspace{5em} $[[{pas} ∩ fv iN]] \cap [[fv nf(iM)]] \subseteq [[{pas} ∩ fv iM ]] = \emptyset$, and}\\ 
      &  \omit\rlap{\hspace{5em} $[[{pas} ∩ fv iN]] \cap [[({pbs} ∩ fv iM)]] \subseteq [[{pas} ∩ fv iM]] = \emptyset$}\\ 
                      &= [[ ord [mu] ({pbs} ∩ fv iM) in nf(iN) ]]
                      && \text{as $[[ [mu] nf(iM) ]] = [[nf(iN)]]$} \\
                      &= [[ ord ({pas} ∩ fv iN) in nf(iN) ]]
                      && \text{$\mu$ is a bijection between}\\
                      & && \text{$[[{pas} ∩ fv iN]]$ and $[[{pbs} ∩ fv iM]]$} \\
                      &= [[ ord {pas} in nf(iN) ]]
                      && \text{from \cref{lemma:fv-nf,corollary:ord-weakening} } \\
                      &= [[ pas' ]]
                      && \text{by the definition of $[[pas']]$} \\
      \end{align*}
    \end{enumerate}
  \item {\nameref{\ottdruleEOneExistsLabel}} Same as for \cref{case:ord-completeness:forall}.
  \item Other rules are congruent, and thus, proved by the corresponding congruent alpha-equivalence rule,
    which is applicable by the induction hypothesis. 
  \end{caseof}
\end{proof}

>>>>

\lemmaNormSoundness*
\begin{proof}
  Mutual induction on $[[nf(iN) = iM]]$ and $[[nf(iP) = iQ]]$.
  Let us consider how this judgment is formed:
  \begin{caseof}
    \item{\ruleref{\ottdruleNrmNVarLabel} and \ruleref{\ottdruleNrmPVarLabel}}\\ By
      the corresponding equivalence rules.
    \item{\ruleref{\ottdruleNrmShiftULabel}, \ruleref{\ottdruleNrmShiftDLabel},
        and \ruleref{\ottdruleNrmArrowLabel}}\\
      By the induction hypothesis and the corresponding congruent equivalence rules.
    \item{\ruleref{\ottdruleNrmForallLabel}}, i.e. $[[nf(∀pas.uN) = ∀pas'.uN']]$ \label{case:norm-soundness:forall}\\
      From the induction hypothesis, we
      know that $[[iN ≈ iN']]$. In particular, by \cref{lemma:equiv-fv}, $[[fv
        iN]] \equiv [[fv iN']]$.
      Then by \cref{lemma:ord-soundness}, $[[{pas'}]]
      \equiv [[{pas} ∩ fv iN']] \equiv [[{pas} ∩ fv iN]]$, and thus,
      $[[{pas'} ∩ fv iN']] \equiv [[{pas} ∩ fv iN]]$.

      To prove $[[∀pas.iN ≈ ∀pas'.iN']]$, it suffices to provide a bijection 
      $\mu : [[{pas'} ∩ fv iN']] \leftrightarrow [[{pas} ∩ fv iN]]$ such that
      $[[iN ≈ [mu]iN']]$. Since these sets are equal, we take $\mu = id$.
    \item{\ruleref{\ottdruleNrmExistsLabel}} Same as for \cref{case:norm-soundness:forall}.
  \end{caseof}
\end{proof}

@@

\lemmaNormalizationCompleteness*
\begin{proof}
  Mutual induction on $[[iN ≈ iM]]$ and $[[iP ≈ iQ]]$.
  \begin{caseof}
  \item {\ruleref{\ottdruleEOneForallLabel}} \label{case:ord-completeness:forall}
   From the normalization definition,
    \begin{itemize}
      \item $[[nf(∀pas.iN)]] = [[∀pas'.nf(iN)]]$ where $[[pas']]$ is $[[ord {pas} in nf(iN)]]$
      \item $[[nf(∀pbs.iM)]] = [[∀pbs'.nf(iM)]]$ where $[[pbs']]$ is $[[ord {pbs} in nf(iM)]]$
    \end{itemize}
    Let us take $[[mu : ({pbs} ∩ fv iM) ↔ ({pas} ∩ fv iN)]]$ from the
    inversion of the equivalence judgment. Notice that from
    \cref{lemma:fv-nf,lemma:ord-soundness}, the domain and the codomain of $\mu$ can be written
    as $[[mu : {pbs'} ↔ {pas'}]]$.

@@

    \item[(ii)] 
    \begin{align*} 
      [[ [mu]pbs' ]] &= [[ [mu] ord {pbs} in nf(iM) ]]
                      && \text{by the definition of $[[pbs']]$ } \\
                      &= [[ [mu] ord ({pbs} ∩ fv iM) in nf(iM) ]]
                      && \text{from \cref{lemma:fv-nf,corollary:ord-weakening} } \\
                      &= [[ ord [mu] ({pbs} ∩ fv iM) in [mu] nf(iM) ]]
                      && \text{by \cref{lemma:distr-mu-ord}, because}\\
      &  \omit\rlap{\hspace{5em} $[[{pas} ∩ fv iN]] \cap [[fv nf(iM)]] \subseteq [[{pas} ∩ fv iM ]] = \emptyset$, and}\\ 
      &  \omit\rlap{\hspace{5em} $[[{pas} ∩ fv iN]] \cap [[({pbs} ∩ fv iM)]] \subseteq [[{pas} ∩ fv iM]] = \emptyset$}\\ 
                      &= [[ ord [mu] ({pbs} ∩ fv iM) in nf(iN) ]]
                      && \text{as $[[ [mu] nf(iM) ]] = [[nf(iN)]]$} \\
                      &= [[ ord ({pas} ∩ fv iN) in nf(iN) ]]
                      && \text{$\mu$ is a bijection between}\\
                      & && \text{$[[{pas} ∩ fv iN]]$ and $[[{pbs} ∩ fv iM]]$} \\
                      &= [[ ord {pas} in nf(iN) ]]
                      && \text{from \cref{lemma:fv-nf,corollary:ord-weakening} } \\
                      &= [[ pas' ]]
                      && \text{by the definition of $[[pas']]$} \\
      \end{align*}
    \end{enumerate}
  \item {\ruleref{\ottdruleEOneExistsLabel}} Same as for \cref{case:ord-completeness:forall}.
  \item Other rules are congruent, and thus, proved by the corresponding congruent alpha-equivalence rule,
    which is applicable by the induction hypothesis. 
  \end{caseof}
\end{proof}
